\vfill A Testing Framework for Web Applications

### 2014-02-06 Paper/paper.tex
Basically nothing but something. Commit between computers.

\subsubsection{\cite{TestingInPractice}}

>>>>

\subsubsection{``Testing Web Applications in Practice'' \cite{TestingInPractice}}
Four students from the University of Seville, Spain published a paper with an overview of web testing. This paper was more of an introduction to testing, outlining the concepts of “Unit Testing”, “Integration Testing”, “Regression Testing”, etc. It also describes how to test an actual web application using open-source software.
